The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-09 rational.tex
the best intro ever written in the entire world

%subcode-inline{bnf-inline} name langRev
%! swap+ = \mathit{swap}^+
%! swap* = \mathit{swap}^*
%! dagger =  ^{\dagger}
%! assocl+ = \mathit{assocl}^+
%! assocr+ = \mathit{assocr}^+
%! assocl* = \mathit{assocl}^*
%! assocr* = \mathit{assocr}^*
%! identr* = \mathit{uniti}
%! identl* = \mathit{unite}
%! dist = \mathit{distrib}
%! factor = \mathit{factor}
%! eta = \eta
%! eps = \epsilon
%! eta+ = \eta^+
%! eps+ = \epsilon^+
%! eta* = \eta^{\times}
%! eps* = \epsilon^{\times}
%! trace+ = trace^+
%! trace* = trace^{\times}
%! ^^^ = ^{-1}
%! (o) = \fatsemi
%! (;) = \fatsemi
%! (*) = \times
%! (+) = +
%! LeftP = L^+
%! RightP = R^+
%! LeftT = L^{\times}
%! RightT = R^{\times}
%! alpha = \alpha

@@

\begin{abstract}
  Every functional programmer knows about sum and product types, {{a+b}} and
  {{a*b}} respectively. Negative and fractional types, $a-b$ and $a/b$
  respectively, are much less known and their computational interpretation is
  unfamiliar and often complicated. We show that in a programming model in
  which information is preserved (such as the model introduced in our recent
  paper on \emph{Information Effects}), these types have particularly natural
  computational interpretations. Intuitively, values of negative types are
  values that flow ``backwards'' to satisfy demands and values of fractional
  types are values that impose constraints on their context.  The combination
  of these negative and fractional types enables greater flexibility in
  programming by breaking global invariants into local ones that can be
  autonomously satisfied by a subcomputation. Furthermore, these types and
  their properties suggest that the previously observed duality of
  computation conflated two orthogonal notions: an additive duality that
  corresponds to backtracking and a multiplicative duality that corresponds
  to unification.
\end{abstract}

@@

start with int times bool divided by bool: it is like an int but it can only
be used as the second component of a pair whose first component is an int;
gives you the power to say here is 20 but you must use it to buy books

To get a feeling for the main idea, consider the following algebraic
manipulation relating a natural number $a$ to itself:
%% \[\begin{array}{rclll}
%% && a & \mbox{initial~$a$} & (0) \\
%% &=& a + 0 & \mbox{$0$~is~identity~for~$+$} & (1) \\
%% &=& a + (-a + a) & \mbox{$-a$~is~the~additive~inverse~of~$a$} & (2) \\
%% &=& (a + (-a)) + a & \mbox{$+$~is~associative} & (3) \\
%% &=& 0 + a & \mbox{$-a$~is~the~additive~inverse~of~$a$} & (4) \\
%% &=& a & \mbox{$0$~is~identity~for~$+$} & (5)
%% \end{array}\]
%% \[\begin{array}{rlllllllll}
%%  \!&\!\!  a \!&\! \!&\!       \!&\! \!&\!    \!&\! \mbox{initial~$a$} \!&\! (0) \\
%% =\!&\!\!  a \!&\!+\!&\!       \!&\!0\!&\!    \!&\! \mbox{$0$~is~identity~for~$+$} \!&\! (1) \\
%% =\!&\!\!  a \!&\!+\!&\! (-a   \!&\!+\!&\! a) \!&\! \mbox{$-a$~is~the~additive~inverse~of~$a$} \!&\! (2) \\
%% =\!&\!\! (a \!&\!+\!&\! (-a)) \!&\!+\!&\! a  \!&\! \mbox{$+$~is~associative} \!&\! (3) \\
%% =\!&\!\!    \!&\!0\!&\!       \!&\!+\!&\! a  \!&\! \mbox{$-a$~is~the~additive~inverse~of~$a$} \!&\! (4) \\
%% =\!&\!\!    \!&\! \!&\!       \!&\! \!&\! a  \!&\! \mbox{$0$~is~identity~for~$+$} \!&\! (5)
%% \end{array}\]

\begin{center}
\scalebox{1.1}{
\includegraphics{diagrams/thesis/algebra-wire1.pdf}
}
\end{center}

Although seemingly pointless, this algebraic proof corresponds, in our model,
to an isomorphism of type {{a <-> a}} with a non-trivial and interesting
computational interpretation. The witness for this isomorphism is a
computation that takes a value of type~$a$ (say \$20.00) and eventually
produces the same \$20.00 value as its output. As the semantics of
Sec.~\ref{sec:rat} formalizes, the intermediate steps of the computation
proceed as follows:
\begin{itemize}
\item We start at line (0) with \$20.00; 
\item We proceed to line (1) with the same \$20.00 but tagged as being in the
  left summand of the type $a+0$; we indicate this value as {{left 20}}
\item We continue to line (2) with the same value {{left 20}};
\item At line (3), as a result of re-association the tag on the \$20.00
  changes to indicate that it is in the left-left summand, i.e., the value is
  now {{left (left 20)}};
\item At line (4), we find ourselves needing to produce a value of type 0
  which is impossible; this signals the beginning of a reverse execution
  which sends us back to line (3) with a value {{left (right 20)}};
\item Execution continues in reverse to line (2) with the value 
  {{right (left 20)}};
\item At line (1) we find ourselves again facing an empty type so we reverse
  execution again; we go to line (2) with a value {{right (right 20)}};
\item We proceed to line (3) and (4) with the value {{right 20}};
\item We finally reach line 5 with the value {{20}}.
\end{itemize}

Now consider the following algebraic manipulation (assuming $a \neq 0$):
%% \[\begin{array}{rclll}
%% && a & \mbox{initial~$a$} & (0) \\
%% &=& a * 1 & \mbox{$1$~is~identity~for~$*$} & (1) \\
%% &=& a * ((1/a) * a) & \mbox{$1/a$~is~the~multiplicative~inverse~of~$a$} & (2) \\
%% &=& (a * (1/a)) * a & \mbox{$*$~is~associative} & (3) \\
%% &=& 1 * a & \mbox{$1/a$~is~the~multiplicative~inverse~of~$a$} & (4) \\
%% &=& a & \mbox{$1$~is~identity~for~$*$} & (5)
%% \end{array}\]

%% \[\begin{array}{rcllllll}
%%  \!&\! a \!&\! \!&\!        \!&\! \!&\!    \!&\! \mbox{initial~$a$} \!&\! (0) \\
%% =\!&\! a \!&\!*\!&\!        \!&\!1\!&\!    \!&\! \mbox{$1$~is~identity~for~$*$} \!&\! (1) \\
%% =\!&\! a \!&\!*\!&\! ((1/a) \!&\!*\!&\! a) \!&\! \mbox{$1/a$~is~the~multiplicative~inverse~of~$a$} \!&\! (2) \\
%% =\!&\!(a \!&\!*\!&\! (1/a)) \!&\!*\!&\! a  \!&\! \mbox{$*$~is~associative} \!&\! (3) \\
%% =\!&\!   \!&\!1\!&\!        \!&\!*\!&\! a  \!&\! \mbox{$1/a$~is~the~multiplicative~inverse~of~$a$} \!&\! (4) \\
%% =\!&\!   \!&\! \!&\!        \!&\! \!&\! a  \!&\! \mbox{$1$~is~identity~for~$*$} \!&\! (5)
%% \end{array}\]

\begin{center}
\scalebox{1.1}{
\includegraphics{diagrams/thesis/algebra-wire2.pdf}
}
\end{center}

As the semantics in Sec.~\ref{sec:rat} formalizes, the witness to this 
{{a <-> a}} isomorphism computes as follows:
\begin{itemize}
\item We start at line (0) with the value {{20}};
\item We proceed to line (1) with the value {{(20,())}};
\item We proceed to line (2) with the value {{(20,((1/alpha),alpha))}} where
  $\alpha$ is essentially a logic variable;
\item We proceed to line (3) with the value {{((20,1/alpha),alpha)}};
\item At line (4) we require that $20$ and $1/\alpha$ cancel each other which
  forces the unification $\alpha=20$, i.e., the value becomes
  {{((20,1/20),20)}} which simplifies to {{((),20)}};
\item We reach line (5) with the value {{20}}.
\end{itemize}

The beauty of the above computation is that it can be realized with a
completely different concurrent schedule as follows. \emph{Simultaneously}
the execution begins at line (0) with the value {{20}}, at line (2) with the
value {{right (right 20)}} flowing forward and the value {{right (left 20)}}
flowing backwards, and at line (3) with the value {{left (left 20)}} flowing
forward and the value {{left (right 20)}} flowing backward. We now have three
independent subcomputations proceeding in parallel: the positive value
created at line (2) which can flow to the consumer; the negative value
created at line (3) which can pay for the debt created at line (2); and the
initial value from line (0) which can flow to the required forward-flowing
value needed at line (3). At some intuitive level, one might understand the
situation as modeling a credit card payment in which money is created at line
(2) for the consumer together with a corresponding debt. The producer's bank
pays for the debt at line (3) and waits for the actual money to arrive from
the producer.

There are at least two fundamental points about this example that must be
emphasized:
\begin{itemize}
\item As the example illustrates, negative types corresponds to ``debts.''
  It would clearly be disastrous if debts could be deleted or
  duplicated. This simple observation explains why negative types are much
  simpler and much more appealing in a framework where information is
  guaranteed to be preserved. In previous work that used negative types (see
  Sec.~\ref{sec:related}), complicated mechanisms are typically needed to
  constrain the propagation and use of negative values because the
  surrounding computational framework is, generally speaking, careless in its
  treatment of information.
\item The appeal of negative types can already be gleaned from the credit
  card analogy. The main reason credit card transactions are convenient is
  because they disentangle the propagation of the resources (money) from the
  propagation of the services. Not every transaction needs both the resources
  and services to be brought together: it is sufficient to have a promise
  that the demand for resources will be somehow satisfied, as long as the
  infrastructure can be trusted with such promises. Computationally, this
  means that negative types allow us to break the dependency between
  producers and consumers and let each compute independently.
\end{itemize}

Instead of also discussing fractional types and related work in this
introduction, we briefly summarize our main technical contributions and move
on to the heart of the paper where these topics can be explained in their
proper context. Our main contributions are:
\begin{itemize}
\item We extend {{langRev}} our reversible programming language of type
  isomorphisms~\cite{rc2011,infeffects} (see Sec.~\ref{sec:pi}) with a notion
  of negative types, that satisfies the isomorphism $a + (-a) = 0$. The
  semantics of this extension is expressed by having a ``dual'' evaluator
  that reverses the flow of execution for negative
  values. (Sec.~\ref{sec:neg})
\item We independently extend {{langRev}} with a notion of fractional types,
  that satisfies the isomorphism $a * (1/a) = 1$. The semantics of this
  extension is expressed by introducing logical variables and a unification
  mechanism to model and resolve the constraints introduced by the fractional
  types. (Sec.~\ref{sec:frac})
\item We combine the above two extensions into one extension that includes
  both negative and fractional types. The resulting language allows any
  rational number to be used as a type. The types satisfy the same familiar
  and intuitive isomorphisms that are satisfied in the mathematical field of
  rational numbers. (Sec.~\ref{sec:rat})
\item We develop programming intuition and argue that negative and fractional
  types ought to be part of the vocabulary of every
  programmer. (Sec.~\ref{sec:prog})
\item We relate our notions of negative and fractional types to previous work
  on continuations. Briefly, we argue that conventional continuations
  conflate negative and fractional components. This observation allows us to
  relate two apparently unrelated lines of work: the first pioneered by
  Filinski~\cite{Filinski:1989:DCI:648332.755574} relating continuations to
  negative types and the second~\cite{Bernardi:2010:CSL:1749618.1749689}
  relating continuations to the fractional types of the Lambek-Grishin
  calculus. (Sec.~\ref{sec:related})
\end{itemize}

>>>>

%subcode-inline{bnf-inline} name langRev
%! swap+ = \mathit{swap}^+
%! swap* = \mathit{swap}^*
%! dagger =  ^{\dagger}
%! assocl+ = \mathit{assocl}^+
%! assocr+ = \mathit{assocr}^+
%! assocl* = \mathit{assocl}^*
%! assocr* = \mathit{assocr}^*
%! identr* = \mathit{uniti}
%! identl* = \mathit{unite}
%! dist = \mathit{distrib}
%! factor = \mathit{factor}
%! eta = \eta
%! eps = \epsilon
%! eta+ = \eta^+
%! eps+ = \epsilon^+
%! eta* = \eta^{\times}
%! eps* = \epsilon^{\times}
%! trace+ = trace^+
%! trace* = trace^{\times}
%! ^^^ = ^{-1}
%! (o) = \fatsemi
%! (;) = \fatsemi
%! (*) = \times
%! (+) = +
%! LeftP = L^+
%! RightP = R^+
%! LeftT = L^{\times}
%! RightT = R^{\times}
%! alpha = \alpha
%! bool = \textit{bool}
%! color = \textit{color}
%! Gr = G

@@

\begin{abstract}
  Every functional programmer knows about sum and product types, {{a+b}} and
  {{a*b}} respectively. Negative and fractional types, $a-b$ and $a/b$
  respectively, are much less known and their computational interpretation is
  unfamiliar and often complicated. We show that in a programming model in
  which information is preserved (such as the model introduced in our recent
  paper on \emph{Information Effects}), these types have particularly natural
  computational interpretations. Intuitively, values of negative types are
  values that flow ``backwards'' to satisfy demands and values of fractional
  types are values that impose constraints on their context.  The combination
  of these negative and fractional types enables greater flexibility in
  programming by breaking global invariants into local ones that can be
  autonomously satisfied by a subcomputation. Theoretically, these types give
  rise to \emph{two} function spaces and to \emph{two} notions of
  continuations, suggesting that the previously observed duality of
  computation conflated two orthogonal notions: an additive duality that
  corresponds to backtracking and a multiplicative duality that corresponds
  to unification.
\end{abstract}

@@

\paragraph*{Negative Types.} 
Consider the following algebraic manipulation relating a natural number $a$
to itself (ignoring the dotted line for a moment):
\begin{center}
\scalebox{1.1}{
\includegraphics{diagrams/thesis/algebra-wire1.pdf}
}
\end{center}
Although seemingly pointless, this algebraic proof corresponds, in our model,
to an isomorphism of type {{a <-> a}} with a non-trivial and interesting
computational interpretation. The witness for this isomorphism is a
computation that takes a value of type~$a$ (say \$20.00) and eventually
produces the same \$20.00 value as its output. As the semantics of
Sec.~\ref{sec:rat} formalizes, this computation flows along the dotted
line with the following intermediate steps:
\begin{itemize}
\item We start at line (0) with \$20.00; 
\item We proceed to line (1) with the same \$20.00 but tagged as being in the
  left summand of the type $a+0$; we indicate this value as {{left 20}}
\item We continue to line (2) with the same value {{left 20}};
\item At line (3), as a result of re-association the tag on the \$20.00
  changes to indicate that it is in the left-left summand, i.e., the value is
  now {{left (left 20)}};
\item At line (4), we find ourselves needing to produce a value of type 0
  which is impossible; this signals the beginning of a reverse execution
  which sends us back to line (3) with a value {{left (right 20)}};
\item Execution continues in reverse to line (2) with the value 
  {{right (left 20)}};
\item At line (1) we find ourselves again facing an empty type so we reverse
  execution again; we go to line (2) with a value {{right (right 20)}};
\item We proceed to line (3) and (4) with the value {{right 20}};
\item We finally reach line 5 with the value {{20}}.
\end{itemize}
The example illustrates that the empty type and negative types have a
fascinating computational interpretation with some flavor of continuations.
What is even more fascinating is that the above computation can be realized
with a completely different concurrent schedule as
follows. \emph{Simultaneously} the execution begins at line~(0) with the
value {{20}}, at line (2) with the value {{right (right 20)}} flowing forward
and the value {{right (left 20)}} flowing backwards, and at line (3) with the
value {{left (left 20)}} flowing forward and the value {{left (right 20)}}
flowing backward. We now have three independent subcomputations proceeding in
parallel: the positive value created at line (2) which can flow to the
consumer; the negative value created at line (3) which can pay for the debt
created at line (2); and the initial value from line (0) which can flow to
the required forward-flowing value needed at line (3). At some intuitive
level, one might understand the situation as modeling a credit card payment
in which money is created at line (2) for the consumer together with a
corresponding debt. The producer's bank pays for the debt at line (3) and
waits for the actual money to arrive from the producer.

There are at least three fundamental points about this example that must be
emphasized:
\begin{itemize}
\item As the example illustrates, negative types corresponds to ``debts.''
  It would clearly be disastrous if debts could be deleted or
  duplicated. This simple observation explains why negative types are much
  simpler and much more appealing in a framework where information is
  guaranteed to be preserved. In previous work that used negative types (see
  Sec.~\ref{sec:related}), complicated mechanisms are typically needed to
  constrain the propagation and use of negative values because the
  surrounding computational framework is, generally speaking, careless in its
  treatment of information.
\item The appeal of negative types can already be gleaned from the credit
  card analogy. The main reason credit card transactions are convenient is
  because they disentangle the propagation of the resources (money) from the
  propagation of the services. Not every transaction needs both the resources
  and services to be brought together: it is sufficient to have a promise
  that the demand for resources will be somehow satisfied, as long as the
  infrastructure can be trusted with such promises. Computationally, this
  means that negative types allow us to break the dependency between
  producers and consumers and let each compute independently.
\item Consider a value of type {{-a + b}}. The above discussion suggests that
  this value demands {{a}} and produces {{b}}, i.e., that it is a
  higher-order funtion mapping {{a}} to {{b}}. Dually and as the underlying
  categorical semantics justifies (see Sec.~\ref{sec:neg}), the same value is
  a continuation which produces {{b}} and then demands {{a}}, which
  introduces a twist on how the function can be used: get the goods {{b}} now
  and pay {{a}} later.
\end{itemize}

\paragraph*{Fractional Types.} 
Consider the following realization of boolean negation written using a
pattern-matching style:
\begin{verbatim}
notB b = case b of 
  False -> True
  True -> False
\end{verbatim}
In a functional language, we are not used to treating the pattern-matching
clauses \verb|False -> True| and \verb|True -> False| as first-class entities
but fractional types allow us to do just that! Informally, we can treat each
of the pattern-matching clauses as a first-class value of type 
{{(1/bool) * bool}}. 
A small but complete example will illustrate the main aspects of this idea.

Let \verb|color| be the datatype with three constructors \verb|R|, \verb|G|,
and \verb|B| and let's try to construct a function that rotates the
colors. In other words, we would like to build the following three
pattern-matching clauses \verb|R -> G|, \verb|G -> B|, and \verb|B -> R|.  In
the algebra of rational numbers we have that for each {{a}} that is not equal
to {{0}}, {{1 = (1/a) * a}}. In our framework this algebraic identity
corresponds to a type isomorphism {{1 <-> (1/a) * a}}. For the datatype
\verb|color|, there are three possible witnesses for this isomorphism mapping
{{()}} to either {{(1/R,R)}} or {{(1/Gr,Gr)}} or {{(1/B,B)}} with the
particular witness determined by further constraints encountered during the
computation. The idea of variables that capture constraints that are
satisfied later is at the heart of logic programming and hence the witness for
the isomorphisms above is generally {{(1/alpha,alpha)}} where~{{alpha}} is a
fresh logic variable.

Returning to our goal of creating the function that rotates the colors, we
proceed as follows:
\begin{itemize}
\item Using the fact that {{1}} is the multiplicative unit, generate from the
  input {{()}} the value {{((),((),()))}} of type {{1 * (1 * 1)}};
\item Apply the isomorphism {{1 <-> (1/a) * a}} in parallel to each of the
  components of the above tuple. The resulting value is 
{{((1/alpha1,alpha1),((1/alpha2,alpha2),(1/alpha3,alpha3)))}} where {{alpha1}},
{{alpha2}}, and {{alpha3}} are fresh logic variables.
\item Using the fact that {{*}} is associative and commutative, we can
  rearrange the above tuple to produce the value:

{{((1/alpha1,alpha2),((1/alpha2,alpha3),(1/alpha3,alpha1)))}}.
\item At this point, we have produced the skeleton for our desired function.
  Assume now that a client uses the first clause of the function in a context
  that contains the value \verb|R|, i.e., the client has the value
  {{((1/alpha1,alpha2),R)}} consiting of one of the clauses of the function
  and an argument. This value can be rearranged to {{((1/alpha1,R),alpha2)}}.
  At this point, we can use the isomorphism {{1 <-> (1/a) * a}} in reverse on
  the first component of the pair which has the following effects:
  \begin{itemize}
    \item the logic variable {{alpha1}} is unified with {{R}};
    \item the first component of the pair then reduces to () and can be
      absorbed by the fact that {{1}} is the multiplicative unit. In other
      words, the value reduces to simply {{alpha2}} reflecting that the
      pattern-matching was successful and the result of the clause is now
      available;
    \item the first clause of the function has now disappeared and the the
      unification adjusts the remaining two clauses to
    {{((1/alpha2,alpha3),(1/alpha3,R))}}.
  \item The same client or another client can now use the second clause
    applying it to {{G}} which would produce the result {{alpha3}} for the
    second client and ground the result of the first client to {{G}}.
  \item Finally the remaining clause {{(1/alpha3,R)}} can be applied to {{B}}
    which grounds the result of the second client to {{B}}.
  \end{itemize}
\end{itemize}
It should be evident that in a universe in which information is not
guaranteed to be preserved by the computational infrastructure, the above
slicing and dicing of functions as a collection of first-class pattern
clauses would make no sense. However, in a computational infrastructure that
is guaranteed to preserve information, computations such as the one above are
guaranteed to ``make sense.'' If one branch uses a clause that matches one
part of the input to produce one part of the output, all other clauses are
automatically adjusted to account for this to ensure that this input is not
matched again and that this output is not produced again. Furthermore, just
like the case for negative types, a dual reading of the the pattern-matching
clauses as continuations allows the context to use the result of the clause
and provide the matching argument later.

\paragraph*{Contributions and Outline.} 
To summarize, in a computational framework that guarantees that information
is preserved, negative and fractional types provide fascinating mechanisms in
which computations can be sliced and diced, decomposed and recomposed,
proceeding forward and backwards, in arbitrary ways. The remainder of the
paper formalizes these informal observations. Specifically our main
contributions are:
\begin{itemize}
\item We extend {{langRev}} our reversible programming language of type
  isomorphisms~\cite{rc2011,infeffects} (see Sec.~\ref{sec:pi}) with a notion
  of negative types, that satisfies the isomorphism $a + (-a) = 0$. The
  semantics of this extension is expressed by having a ``dual'' evaluator
  that reverses the flow of execution for negative
  values. (Sec.~\ref{sec:neg})
\item We independently extend {{langRev}} with a notion of fractional types,
  that satisfies the isomorphism $a * (1/a) = 1$. The semantics of this
  extension is expressed by introducing logical variables and a unification
  mechanism to model and resolve the constraints introduced by the fractional
  types. (Sec.~\ref{sec:frac})
\item We combine the above two extensions into one extension that includes
  both negative and fractional types. The resulting language allows any
  rational number to be used as a type. The types satisfy the same familiar
  and intuitive isomorphisms that are satisfied in the mathematical field of
  rational numbers. (Sec.~\ref{sec:rat})
\item We develop programming intuition and argue that negative and fractional
  types ought to be part of the vocabulary of every
  programmer. (Sec.~\ref{sec:prog})
\item We relate our notions of negative and fractional types to previous work
  on continuations. Briefly, we argue that conventional continuations
  conflate negative and fractional components. This observation allows us to
  relate two apparently unrelated lines of work: the first pioneered by
  Filinski~\cite{Filinski:1989:DCI:648332.755574} relating continuations to
  negative types and the second~\cite{Bernardi:2010:CSL:1749618.1749689}
  relating continuations to the fractional types of the Lambek-Grishin
  calculus. (Sec.~\ref{sec:related})
\end{itemize}

% Now consider the following algebraic manipulation (assuming $a \neq 0$):
% \begin{center}
% \scalebox{1.1}{
% \includegraphics{diagrams/thesis/algebra-wire2.pdf}
% }
% \end{center}
% As the semantics in Sec.~\ref{sec:rat} formalizes, the witness to this 
% {{a <-> a}} isomorphism computes as follows:
% \begin{itemize}
% \item We start at line (0) with the value {{20}};
% \item We proceed to line (1) with the value {{(20,())}};
% \item We proceed to line (2) with the value {{(20,((1/alpha),alpha))}} where
%   $\alpha$ is essentially a logic variable;
% \item We proceed to line (3) with the value {{((20,1/alpha),alpha)}};
% \item At line (4) we require that $20$ and $1/\alpha$ cancel each other which
%   forces the unification $\alpha=20$, i.e., the value becomes
%   {{((20,1/20),20)}} which simplifies to {{((),20)}};
% \item We reach line (5) with the value {{20}}.
% \end{itemize}
